### 2023-12-14 experiments/notebooks/figures1and3.qmd
all charts in paper recreated

@@

@@

```{julia}
outcome = Serialization.deserialize("results_extra/mnist_outcome.jls")
```

>>>>

This notebook can be used to recreate Figures 1 and 3 in the main paper.

@@

The code below generates Figure 1 in the main paper.

@@

The code below generates Figure 3 in the main paper. This uses the results from this [release](https://github.com/pat-alt/ECCCo.jl/releases/tag/results-camera-ready).

```{julia}
# Using results from: https://github.com/pat-alt/ECCCo.jl/releases/tag/results-camera-ready
outcome = Serialization.deserialize("results/mnist_outcome.jls") # results from 
factual = 3
target = 5
seed = 3333 
plt, ces = compare_counterfactuals(
    outcome; factual=factual, target=target,
    seed = seed
)
savefig(plt, joinpath(paper_figpath, "mnist_benchmark.png"))
CounterfactualExplanations.target_probs.(ces)
```
